Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-02-04 Paper/Manuscript.tex
Updated chapter IIa-c

The controlling computer program generates a short-duration digital transmit signal (a ping), $\ytx(\samplesymt)$, where $\samplesymt$ is a sample index in the discrete time domain. Typical BB pulses are linear upsweep pulses windowed by an envelope function. In the EK80 a linear sweep enveloped by a Hann function is implemented (Fig.~\ref{fi:ytx}. This is found in the class \verb|Core.EK80Calculation.generateIdealWindowedSendPulse|, where the parameters 'f0', 'f1', tau, fs and slope are the initial frequency, the final frequency, the pulse duration, the sampling rate, and the proportion of the signal that is tapered in each end, respectively. A slope of 0 and .5 indicates no tapering and tapering across the whole signal, respectively.

To generate the signal

The generated signal $\ytxe(\timesym)$ is converted to an analogue electric signal and amplified by the transceiver to obtain analogue signal $\ytxe(\timesym)$. The analogue and amplified signal is passed on to the transducer to generate the transmitted acoustic signal $\ytxa(\timesym)$ in the water column, where $\timesym$ is the time for the (analog) signal. For a split-aperture echosounder system, there are typically three or four channels to allow estimation of the angle of arriving echoes, and the signal is typically transmitted with equal power across the channels.

\begin{figure}
\includegraphics[width=16cm]{Fig_ytx}
\caption{\label{fi:ytx} Ideal and enveloped send pulse between 34kHz to 45kHz with a slope of 0.057, as implemented in the EK80. The orange curve illustrate the effect of setting the slope to 0.5.}
\end{figure}

>>>>

The controlling computer program generates a short-duration digital transmit signal (a ping), $\ytx(\samplesymt)$, where $\samplesymt$ is a sample index in the discrete time domain. Typical BB pulses are linear upsweep pulses windowed by an envelope function. The generated signal $\ytxe(\timesym)$ is converted to an analogue electric signal and amplified by the transceiver to obtain analogue signal $\ytxe(\timesym)$. The analogue and amplified signal is passed on to the transducer to generate the transmitted acoustic signal $\ytxa(\timesym)$ in the water column, where $\timesym$ is the time for the (analog) signal. For a split-aperture echosounder system, there are typically three or four channels to allow estimation of the angle of arriving echoes, and the signal is typically transmitted with equal power across the channels.

In the example a linear sweep enveloped by a Hann function is implemented (Fig.~\ref{fi:ytx}). This is found in the class \verb|Core.EK80Calculation.generateIdealWindowedSendPulse|, where the parameters are the initial frequency, the final frequency, the pulse duration, the sampling rate, and the proportion of the signal that is tapered in each end, respectively. A tapering of 0 and .5 indicates no tapering and tapering across the whole signal, respectively.
\begin{figure}
\includegraphics[width=16cm]{Fig_ytx}
\caption{\label{fi:ytx} Ideal and enveloped send pulse between 34kHz to 45kHz with a slope of 0.057, as implemented in the EK80. The orange curve illustrate the effect of setting the slope to 0.5.}
\end{figure}
